Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-15 draft_v2.Rmd
update

```{r}
# changes in request volume after covid by categories 
diff = dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,CATEGORY) %>%
  count() %>% 
  dcast(CATEGORY~CREATEYR) %>% 
  mutate(diff = `2020`-`2019`,
         diff_pchg = `2020`/`2019` )
```

>>>>

```{r}
# changes in request volume after covid by categories 
diff = dat %>% 
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CREATEYR,CATEGORY) %>%
  count() %>% 
  dcast(CATEGORY~CREATEYR) %>% 
  mutate(diff = `2020`-`2019`,
         diff_pchg = `2020`/`2019` )
```
summary statistics

```{r}
#summary stats
